quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-06-24 paper-quollr.Rmd
Function with arrange RMSE and 2D layouts
Add the code

```{r limb-rmse, fig.cap="Assessing which of the 6 NLDR layouts on the limb muscle data is the better representation using RMSE for varying binwidth ($a_1$). Colour  used for the lines and points in the left plot and in the scatterplots represents NLDR layout (a-f). Layout d is perform well at large binwidth (where the binwidth is not enough to capture the data struture) and poorly as bin width decreases. Layout f is the best choice.\\label{fig:limb-rmse}", fig.pos='H'}

error_plot_limb + 
  wrap_plots(nldr1, nldr2, nldr3, 
  nldr4, nldr5, nldr6, ncol = 2) 
```

>>>>

```{r limb-rmse, fig.cap="Assessing which of the 6 NLDR layouts on the limb muscle data is the better representation using RMSE for varying binwidth ($a_1$). Colour  used for the lines and points in the left plot and in the scatterplots represents NLDR layout (a-f). Layout d is perform well at large binwidth (where the binwidth is not enough to capture the data struture) and poorly as bin width decreases. Layout f is the best choice.\\label{fig:limb-rmse}", fig.pos='H', echo=TRUE}

design <- gen_design(n_right = 6, ncol_right = 2)

plot_rmse_layouts(plots = list(error_plot_limb, nldr1, 
                               nldr2, nldr3, nldr4, 
                               nldr5, nldr6), design = design)
```
